### 2019-01-02 Sections/models_for_quantum_computation.tex
tiny edits

If we have in the circuit model an $n$-partical pure state $\ket{\psi}$, acted upon by $U$ with depth $L$,
% 
a time-dependent Hamiltonian $\hat{H}(t)$ is universal if the ground state of $\hat{H}(t_f)$ is equal to $\hat{U}\ket{\psi}$ with non-zero probability, the number of particles in $H(t_f)$ is polynomial in $n$ and $L$, and $t_f$ is polynomial in $n$ and $L$.

It has been proven that AQC can efficiently simulate the entire circuit model \cite{bib:RevModPhys.90.015002}, which implies that it is itself universal for efficient quantum computing.

>>>>

If we have in the circuit model an $n$-partical pure state $\ket{\psi}$, acted upon by $U$ with depth $L$, a time-dependent Hamiltonian $\hat{H}(t)$ is universal if:
\begin{itemize}
\item The ground state of $\hat{H}(t_f)$ is equal to $\hat{U}\ket{\psi}$ with non-zero probability.
\item The number of particles in $H(t_f)$ is polynomial in $n$ and $L$, and $t_f$ is also polynomial in $n$ and $L$.
\end{itemize}
It has been proven that AQC can efficiently simulate the entire circuit model \cite{bib:RevModPhys.90.015002}, which implies that it is itself universal for efficient quantum computing.
